Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-08-22 Thesis/chapter/03-theoretical-background.tex
aestetic

@@

\subsection{Photovoltaics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable option is \gls{pv}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Materials and Their Analysis}
\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ds{
introduction 
    why I chose this practicum, 
        bcs wanted to check if lab is for me 
    why i chose to include ml 
        bcs I wanted what i learned during undergrad courses help me find a good solution and 
        wanted to dive deeper into the ml field as it is very interesting for 
what is ML? 
what kind of ML techniques? 
statistics:
what is the difference between ml and stat? 
    superficially very similar but different goals and diff rahmenbedingungen 
DOE is a very old, much information less experiments 
    how to design experiment: already many insights for next time 
statistics: 
    help me find insight from data 
    ANOVA 
    linear regression 
}

\subsection{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Why introduce machine learning to this project? 
I wanted to apply and delve into what I've been studying during my undergrad courses. 
This seemed like the perfect oppurtunity.

\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
%For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
It is easy for humans to come up with question to detect an AI, 
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.

@@

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}
\url{https://rss.onlinelibrary.wiley.com/doi/abs/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}

@@

\subsubsection{Learning from Data}
General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
\begin{enumerate}
	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions
\end{enumerate}
\textbf{1. Statement of the Problem} There was no clear statement of the problem. Now I would formulate it: "How to produce most insulating layer with least energy? How do we define most insulating?" That's why there are two output variables rather than one.
\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
\textbf{3. Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting. The data collection can affect the sampling distribution and influence the next steps. 
\textbf{4. Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection. Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task. Feature selection: A small number of informative features make the task of estimating dependencies easier. 
\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables. 
\cite{cherkassky1998learning}

@@

\subsubsection{2022-06-19-Free-Writing}
The problem which presents it self is in principle a search problem.
A large space of possible combinations of experimental anordnungen presents it self
and out of these we want to find the optimial parameter combination. 
The best way with unlimitied resources would be the brute-force approach to try every possibility. 
But due to limited time this is unfeasable. 
But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
What are the upper and lower limits and which intervals/step size/grid size should be used. 
Also even before, we have to answer which dimensions/parameters should we include in the search? 
Which parameters should we keep constant and at which value? 
And finally which features should we use to measure the goodness of an experiment?

@@

\subsubsection{things I should try if they work:}
\begin{itemize}
    \item GA 
    \item what is reinforcement learning? 
    \item PCA
    \item linear regression
    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
\end{itemize}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics}
%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable option is \gls{pv}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Materials and Their Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning and Statistics}
\ds{
introduction 
    why I chose this practicum, 
        bcs wanted to check if lab is for me 
    why i chose to include ml 
        bcs I wanted what i learned during undergrad courses help me find a good solution and 
        wanted to dive deeper into the ml field as it is very interesting for 
what is ML? 
what kind of ML techniques? 
statistics:
what is the difference between ml and stat? 
    superficially very similar but different goals and diff rahmenbedingungen 
DOE is a very old, much information less experiments 
    how to design experiment: already many insights for next time 
statistics: 
    help me find insight from data 
    ANOVA 
    linear regression 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Why introduce machine learning to this project? 
I wanted to apply and delve into what I've been studying during my undergrad courses. 
This seemed like the perfect oppurtunity.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Artificial Inteligence and Machine Learning}
%How can \gls{ai} and \gls{ml} be defined? 
The history of \gls{ai} goes back to the middle of the \nth{20} century. 
Researchers from the emerging field came together at the Dartmouth conference and the term "\gls{ai}" was coined\cite{McCarthy1955}. 
\Gls{ai}'s  history is beautifully depicted by McCorducks' 1982 book "Machines Who Think"\cite{McCorduck1982,Apter1982}, which focuses on the great minds behind the advances.
%For a more in depth dive into the history of AI consult the beautifully written review\cite{Apter1982} of McCorduck's 1982 book "Machines Who Think"\cite{McCorduck1982}, which focuses also on the great minds behind advances of \gls{ai}.
Pioneers like Alan Turing thought a lot about how to define, test and implement \gls{ai}\cite{Howard2019}. 
One example how to measure \gls{ai} is to let it play chess against a human\cite{Silver2017} 
(in 1997 a chess computer called Deep Blue won against the World Chess Champion Garry Kasparov for the first time\cite{Feng1999}).
Another test ingenioused by Alan Turing, is that a human communicates with an unknown entity (in written form) and must judge if they are dealing with a machine or a human being. 
It is easy for humans to come up with question to detect an AI, 
but when reading AI written articles\cite{gpt2020}, it's easy to see this test being passed in the near future.

@@

DOEs: randomization, latin square, orthogonal experiment design, full/2-lvl factorial design, placket burman, 
\url{https://www.jstor.org/stable/2238570}\cite{karlin1966optimal}\\
\url{https://doi.org/10.1111/j.2517-6161.1973.tb00944.x}\cite{whittle1973some}
maybe \url{https://www.sciencedirect.com/science/article/pii/S0167715212003343?via\%3Dihub}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Learning from Data}
General experimental procedure from Cherkassky and Mulier\cite{cherkassky1998learning}
\begin{enumerate}
	\item State the problem 
	\item Formulate the hypothesis
	\item Design the experiment/generate the data
	\item Collect the data and perform preprocessing
	\item Estimate the model 
	\item Interpret the model/draw the conclusions
\end{enumerate}
\textbf{1. Statement of the Problem} There was no clear statement of the problem. Now I would formulate it: "How to produce most insulating layer with least energy? How do we define most insulating?" That's why there are two output variables rather than one.
\textbf{2. Hypothesis Formulation} formulate an unknown dependency and define input and output variables.
\textbf{3. Data Generation and Experiment Design} can be either in control of the modeler (designed experiment) or in an observational setting. The data collection can affect the sampling distribution and influence the next steps. 
\textbf{4. Collect the Data and Perform Preprocessing} here outliers are detected and data preprocessing/encoding/feature selection. Scaling by standard deviation might be a good idea, but independent scaling of variables can lead to suboptimal representation for the learning task. Feature selection: A small number of informative features make the task of estimating dependencies easier. 
\textbf{5. Model Estimation} The main goal is to construct a model for accurate prediction of future outputs
\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables. 
\cite{cherkassky1998learning}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{2022-06-19-Free-Writing}
The problem which presents it self is in principle a search problem.
A large space of possible combinations of experimental anordnungen presents it self
and out of these we want to find the optimial parameter combination. 
The best way with unlimitied resources would be the brute-force approach to try every possibility. 
But due to limited time this is unfeasable. 
But a new questions arises: how should the ausmasse of the search space be eingeschraenkt? 
What are the upper and lower limits and which intervals/step size/grid size should be used. 
Also even before, we have to answer which dimensions/parameters should we include in the search? 
Which parameters should we keep constant and at which value? 
And finally which features should we use to measure the goodness of an experiment?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{things I should try if they work:}
\begin{itemize}
    \item GA 
    \item what is reinforcement learning? 
    \item PCA
    \item linear regression
    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
\end{itemize}

@@

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
